---
title: "&nbsp;"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    css: custom.css
---

<script>
  $(document).ready(function() {
    $('#TOC').parent().prepend('<div id=\"nav_logo\"><img src=\"myimage.png\"></div>');
  });
</script>

<style>
#nav_logo {
  border-radius: 50%;
  width: 100%;
  margin-top: 20px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css, echo = FALSE}

.section.level2 {
  display: none;
}

```

```{js, echo = FALSE}

$(document).ready(function () {

  $('.section.level2:first').show();

});

// force this to wait till all the other js is loaded
$(window).on('load', function() {

  $('.tocify-item.list-group-item').click(function(event){

    $('.section.level2').hide();

    var id = $(this).data('unique');

    $('#'+id).show();

  });

});
  
```

## Expertise {#Expertise}

- Expertise in analyzing and coordinating data, generating reports, tables, listings and graphs in either HTML, PDF or RTF formats according to the client specifications using SAS/R/Python.

- Extensive use of [SQL to perform queries, join tables, etc.]()

- Working on different libraries [pandas, numpy, sklearn, statsmodels, etc.](https://pandas.pydata.org)
in python.

- Data Visualization using [matplotlib](), [seaborn](), [plotly](), [cufflinks]() in python
and [ggplot2, plotly]() using R

- Dashboard Preparation using [Shiny](), Power BI and Tableau

- Extensive knowledge of statistical techniques--Linear and Logistic
Regression, GLM, Factor analysis, Support Vector Machines, Multivariate
Analysis, Stochastic modeling.

- Text Analytics, Data Mining techniques (Clustering, Classification, Association), Market Basket Research using R

- Fuzzy matching, Predictive modeling and building efficient algorithms using machine learning techniques in python

- Packages:



## Tools {#Tools}

<img src = "https://github.com/devicons/devicon/blob/master/icons/rstudio/rstudio-original.svg" 
height = "40"
width = "40" />

```{r cars}
summary(cars)
```

## Including Plots {#Including_Plots}

