---
title: "&nbsp;"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    css: custom.css
---

<script>
  $(document).ready(function() {
    $('#TOC').parent().prepend('<div id=\"nav_logo\"><img src=\"myimage.png\"></div>');
  });
</script>

<style>
#nav_logo {
  border-radius: 50%;
  width: 100%;
  margin-top: 20px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css, echo = FALSE}

.section.level2 {
  display: none;
}

```

```{js, echo = FALSE}

$(document).ready(function () {

  $('.section.level2:first').show();

});

// force this to wait till all the other js is loaded
$(window).on('load', function() {

  $('.tocify-item.list-group-item').click(function(event){

    $('.section.level2').hide();

    var id = $(this).data('unique');

    $('#'+id).show();

  });

});
  
```

## Expertise {#Expertise}

- Expertise in analyzing and coordinating data, generating reports, tables, listings and graphs in either HTML, PDF or RTF formats according to the client specifications using SAS/R/Python.

- Extensive use of [SQL to perform queries, join tables, etc.]()

- Working on different libraries [pandas, numpy, sklearn, statsmodels, etc.](https://pandas.pydata.org)
in python.

- Data Visualization using [matplotlib](), [seaborn](), [plotly](), [cufflinks]() in python
and [ggplot2, plotly]() using R

- Dashboard Preparation using [Shiny](), Power BI and Tableau

- Extensive knowledge of statistical techniques--Linear and Logistic
Regression, GLM, Factor analysis, Support Vector Machines, Multivariate
Analysis, Stochastic modeling.

- Text Analytics, Data Mining techniques (Clustering, Classification, Association), Market Basket Research using R

- Fuzzy matching, Predictive modeling and building efficient algorithms using machine learning techniques in python

## Tools {#Tools}

<img src = "https://d33wubrfki0l68.cloudfront.net/1ac3f0e3753f18c7e2a8893957d1841fba1e3d08/48a33/wp-content/uploads/2018/10/rstudio-logo-flat.png" 
height = "40"
width = "100" />
<img src = "https://upload.wikimedia.org/wikipedia/commons/thumb/1/10/SAS_logo_horiz.svg/2560px-SAS_logo_horiz.svg.png" 
height = "40"
width = "100" />
<img src = "https://upload.wikimedia.org/wikipedia/commons/thumb/f/f8/Python_logo_and_wordmark.svg/2560px-Python_logo_and_wordmark.svg.png" 
height = "40"
width = "120" />
<img src = "https://upload.wikimedia.org/wikipedia/commons/8/87/Sql_data_base_with_logo.png" 
height = "40"
width = "100" />
<img src = "https://cdn.icon-icons.com/icons2/2699/PNG/512/microsoft_powerbi_logo_icon_169958.png" 
height = "60"
width = "120" />
<img src = "https://upload.wikimedia.org/wikipedia/commons/4/4b/Tableau_Logo.png" 
height = "40"
width = "140" />

```{r, echo=FALSE,eval=TRUE,warning=FALSE,message=FALSE}
library(plotly)
z <- data.frame (tools = c('SAS','R','Python','SQL','Power BI','Tableau'),
                 rating = c(5,5,4,4,3,3))

plot_ly(z, y = ~rating, x = ~tools, type = 'bar', color = I('black')) %>%
  layout(title = "Proficiency Rating",
         xaxis = list(title = "", tickfont = list(size = 14)), 
         yaxis = list(title = "", showgrid = FALSE)
         )

```


## Education {#Education}



